---
title: "Exploratory_data_analysic_project"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown


## kicstarter dataset
 i this data exploration i am uding kick starter data set
```{r cache=TRUE}
kick_data=read.csv("/media/kuldeep/seed2/kicstrter_data/ks-projects-201801.csv")
names(kick_data)

```
now we know that what is inside the data we will do univariate visulisation firstl 
```{r echo=FALSE, fig.align='center', message=TRUE, warning=TRUE, paged.print=TRUE}

library(ggplot2)
library(dplyr)
```
 now we plot the bar graph for knowinkg that which country is making more project using kickstarter
```{r echo=FALSE}
ggplot(data = kick_data,aes(x=country))+geom_bar()+ggtitle("countries participating in kickstarter",subtitle ="generated by kickstarter data" )+xlab("countries")+ylab("NO. Of Projects")
```
 now we will find tha

```{r echo=FALSE, fig.align='center', fig.cap="generated", message=FALSE, warning=FALSE, paged.print=TRUE}
library(plotly)
library(scales)
as=c(0:500000)
a=ggplot(data = kick_data,aes(x=country))+geom_bar()+xlab("countries")+ylab("NO. Of Projects")+scale_y_continuous(labels =comma)
ggplotly(a)
```
 now we will se that whic category is having more success so we will plot a count plot between category vs sucess
```{r echo=FALSE}
a=ggplot(data=kick_data,aes(x=main_category,y=state))+geom_count()+theme()
ggplotly(a)
```
 
## Analysi between fund raised and country
 now let us see that how much fund did each startup rise vs country also we will consider that the startup become sucessful,cancelled or fall into some other category
```{r echo=FALSE}
jpeg("figure.jpeg")
ggplot(data=kick_data,aes(x=factor(country),y=usd_goal_real,colour=state))+geom_boxplot()+scale_y_continuous(labels = comma)+coord_cartesian(ylim = c(0,5000000))
dev.off()
```
 as from this we can easily say that those whose goal is too high all of them not definately sucessful
 there is only one case is usa that a person havin a hogh goal had sucessfully achived it
## US DATA EVALUATION
below is given a plot of us data from the whole data of kick starter
#1we can ask the question that how much funding is required for a successful project?
#2 can also ask question that how much backers are required to get real pledge?

for this we have plotted the graph between the no of backers and usd_pledged_real 
 
```{r}
us_data=kick_data%>%filter(country=="US")
as=ggplot(data=us_data,aes(x=usd_pledged_real,y=backers,colour=state))+geom_point()+scale_x_continuous(labels = comma)+coord_cartesian(ylim = c(0,10000),xlim = c(0,2500000))

ggplotly(as)
```
 
 
